---
title: ""
author: ""
date: ""
output: word_document
---
  
```{r, echo = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# `r reg.order[r]` - `r category0 ` Analsys Notes

This analysis uses nationally collected landings data for the `r ifelse(reg.order[r] %in% "National", "whole U.S.", paste0("for the", reg.order[r], "region")) `, downloaded from the NOAA FOSS site <https://foss.nmfs.noaa.gov/apexfoss/f?p=215:200::::::>. 

##Warnings/FYIs

```{r, echo = FALSE, warnings = FALSE}
print(warnings.list0)
```

## The number of species in origional data, used in the analysis, and removed from the analysis: 
```{r, echo = FALSE, warnings = FALSE}
spptable0[,-1] %>%
    knitr::kable(row.names = T, booktabs = T)
```

## Species in Each category by Common Name

"pre" is for species in the origional data
"pst" are the species that were used in the final anlaysis
```{r, echo = FALSE}
spp.output
```

## Negative values?

### Dollars

```{r, echo = FALSE, warning = FALSE}
a0<-landings.data#[idx,]
a0[(a0$Dollars<0 & !(is.na(a0$Dollars))),] %>%
    knitr::kable(row.names = F, booktabs = T)
```

### Pounds

```{r, echo = FALSE, warning = FALSE}
a0<-landings.data#[idx,]
a0[(a0$Pounds<0 & !(is.na(a0$Pounds))),] %>%
    knitr::kable(row.names = F, booktabs = T)
```