---
title: "Productivity Index - Input"
author: "Emily Markowitz"
date: "Feb. 05, 2020"
output: 
  pdf_document:
    toc: true
    toc_depth: 4
    number_sections: true
    df_print: kable
---

```{r setup, include=FALSE, echo = FALSE, message  = FALSE}
# knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=FALSE)
```


```{r, echo = FALSE, include=FALSE, echo = FALSE, message  = FALSE}
options(scipen=10000)

ln<-log #tricky, tricky, Base R! Didn't fool me this time!!!

####COLOR PALLET#####
#mostly for figures
NOAALightBlue<-"#C9E1E6"
NOAADarkBlue<-"#0098A6"
NOAADarkGrey<-"#56575A" #text
NOAABlueScale<-colorRampPalette(colors = c(NOAALightBlue, NOAADarkBlue))

dir.data<-paste0(dirname(getwd()), "/Data/")
```

#Math Theory: General Total Factor Productivity ($TFP$) Equation

The general form of the $TFP$ can be measured as aggregate output ($Y$) divided by real total inputs ($X$). Rates of TFP growth are constructed using the Törnqvist index approach. The TFP growth over two time periods is defined as:

$$ln(TFP_t/TFP_{t-1}) = \sum_{i=1}^n((\frac{R_{i,t} + R_{i,t-1}}{2}) * ln(\frac{Y_{i,t}}{Y_{i,t-1}}))) - \sum_{j=1}^m((\frac{W_{j,t} + W_{j,t-1}}{2}) * ln(\frac{X_{j,t}}{X_{j,t-1}})))$$

Such that:
 
 - Output  = $\sum_{i=1}^n((\frac{R_{it} + R_{it-1}}{2}) * ln(\frac{Y_{it}}{Y_{it-1}}))$

 - Input = $\sum_{j=1}^n((\frac{W_{jt} + W_{jt-1}}{2}) * ln(\frac{X_{jt}}{X_{jt-1}}))$

where: 

 - $Y_i$ are individual outputs. This will later be refered to as $Q_i$ in the following equations. 
 
 - $X_j$ are individual inputs
 
 - $R_i$ are output revenue shares
 
 - $W_j$ are input cost shares
 
 - $t$ and $t-1$ are time subscripts, where 1 is the minimum year in the dataset
 
 - $i$ is category, e.g., Finfish (=1), Shellfish (=2)

 - $s$ is species, e.g., Salmon, Alewife, Surf Clams

-------

#Output Method: From Price to Quantity Measures

###Variable Summary

Variables

 - $Q$ are individual quantity outputs in pounds (lbs). 
 
 - $V$ are individual value outputs in dollars ($)

 - $R$ are output revenue shares
 
 - $P$ are prices

 - $PC$ are price changes
 
 - $PI$ are price indicies, often defined by a price from a base year $baseyr$
 
 - $baseyr$ is the year to base all indicides from
 
 
 Inidicies
 
 - $t$ and $t-1$ are time subscripts, where 1 is the minimum year in the dataset
 
 - $i$ is category, e.g., Finfish (=1), Shellfish (=2)

 - $s$ is species, e.g., Salmon, Alewife, Surf Clams
 

#Input Method: From Price to Quantity Measures

 - Input = $\sum_{j=1}^n((\frac{W_{jt} + W_{jt-1}}{2}) * ln(\frac{X_{jt}}{X_{jt-1}}))$

###Variable Summary

Variables

 - $Q$ are individual quantity outputs in pounds (lbs). 
 
 - $V$ are individual value outputs in dollars ($)

 - $W$ are weights of the data to the portion
 
 - $P$ are prices

 - $PC$ are price changes
 
 - $PI$ are price indicies, often defined by a price from a base year $baseyr$
 
 - $baseyr$ is the year to base all indicides from
 
 
 Inidicies
 
 - $t$ and $t-1$ are time subscripts, where 1 is the minimum year in the dataset
 
 - $i$ is category, e.g., Finfish (=1), Shellfish (=2)


categories

 - Capital (K): Length of the vessel times the percent time spent in the fishery. Some vessels spend time in more than one fishery.

 - Labor Input (L): Crew Size * Days at Sea. 

 - Energy (E): Estimated quantity based on econometric models.

 - Materials (M): Estimated quantity of bait and ice based on econometric models.

 - Service (S)

###Data requirements

We need time series data for the price of all categories ($P_{t}$; e.g., Total), price of each category (i) ($P_{i=1}$; e.g., K, L, E, M, and S), and the quantity of each category (i) ($Q_{i=1}$; e.g., K, L, E, M, and S):

#### Edit Data

We amy not have information for each of the K, L, E, M, and S categories, so the code has to be dynamic enough to only take for the data that is available. 

```{r, echo = TRUE, warning = FALSE}
temp<-read.csv(file = paste0(dir.data, "Tornqvist Index-Calculations_InputEx.csv"))
rownames(temp)<-temp$year
temp$year<-NULL

temp.q<-temp[,grepl(pattern = "Q", x = names(temp))]
temp$QE0_0Total<-rowSums(temp.q, na.rm = T)

temp<-orgional.data<-cbind.data.frame(temp)

```


```{r, echo  = FALSE}
temp %>%
    knitr::kable(row.names = T, booktabs = T)
```


#### The nameing conventions of the column names. 

For example, in "V0_0Total":

 - "V"... refers to the variable represented in the column (here V = "Value")
 
 - ..."0"... refers to the whole fishery
 
  - ..."_"... is simply a seperator in the title
 
 - Since this is the total, ..."0".. refers to the index of the species, which is not relevant since this is the sum of the category, hense = 0
 
 - ..."Total" is purely descriptive (here the total for the fishery), so you can follow along with what is happening!
 
 
Similarly for "Q2_0K": 

 - "Q"... refers to the variable represented in the column (here Q = "Quantity")
 
 - ..."2"... refers to the category index (here, = Capital (K))
 
 - ..."_"... is simply a seperator in the title
 
 - ..."0".. refers to the index of the input value, here these are the total (= 0). 
 
 - ..."K" is purely descriptive (here the name of the species), so you can follow along with what is happening!


Here I am just going to do some housekeeping items

```{r, echo  = TRUE}
    NameBaseTotal<-substr(x = names(temp)[grep(x = names(temp), pattern = "0Total")][1], 
                        start = 3, stop = nchar(names(temp)[grep(x = names(temp), 
                                                                 pattern = "0Total")][1]))

    # Find which columns in this table are quantity Columns - we will need this for later
    QColumns<-grep(pattern = paste0("Q[0-9]+"), 
                 x = names(temp))
    
    # Find which columns in this table are price Columns - we will need this for later
    PColumns<-grep(pattern = paste0("P[0-9]+"), 
                 x = names(temp))
    
      # Find which columns in this table are value Columns - we will need this for later
  VColumns<-rep_len(x = "", length.out = length(QColumns))
  for (j in 1:length(VColumns)){
    VColumns[j]<-paste0("V", substr(x = names(temp)[QColumns[j]], 
                                    start = 2, 
                                    stop = nchar(names(temp)[QColumns[j]])))
  }
  
```


###Value for each category ($V_{i,t}$; e.g., K, L, ...)
We first calculate the value for each input category. 

Price for a species (s) of category (i) in year (t) = 
$$V_{i,t} = VP_{i,t}*/*Q_{i,t}$$

where: 

 - $P_{i,t}$ is the price per category (i), for each year (t)
 
 - $Q_{i,t}$ is the quantity per category (i), for each year (t)
 
 - $V_{i,t}$ is the value ($) per category (i), for each year (t)

Here we calculate the value for each category
```{r, echo  = TRUE}
#####Value for each category#####
tempV<-data.frame(data = rep_len(x = NA, length.out = nrow(temp)))
for (c in 1:length(PColumns)) {
  
    NameBase<-substr(start = 2, 
                   stop = nchar(names(temp)[PColumns[c]]), 
                   x = names(temp)[PColumns[c]]) 
    
    Q0<-temp[,names(temp) %in% paste0("Q", NameBase)]
    P0<-temp[,names(temp) %in% paste0("P", NameBase)] #to make sure its the same column
  tempV[,c]<-P0*Q0
  names(tempV)[c]<-paste0("V", NameBase ) #name the column
}

tempV<-data.frame(tempV)
temp<-cbind.data.frame(temp, tempV)
```

```{r, echo  = FALSE}
temp0<-cbind.data.frame("Other..." = rep_len(x = "...", length.out = nrow(temp)), 
                 temp[,(ncol(temp)-4):ncol(temp)])
temp0 %>%
    knitr::kable(row.names = T, booktabs = T)
```


###Sum value of the the fishery

$$V_t = \sum_{i=1}^{m} V_{i,t}$$

where: 

 - $V_{t}$ is the value of the fishery by year

```{r, echo  = TRUE}
temp[,ncol(temp)+1]<-rowSums(tempV, na.rm = T)
names(temp)[ncol(temp)]<-paste0("V", NameBaseTotal) #name the column
```

```{r, echo  = FALSE}
temp0<-cbind.data.frame("Other..." = rep_len(x = "...", length.out = nrow(temp)), 
                 temp[,(ncol(temp)-4):ncol(temp)])
temp0 %>%
    knitr::kable(row.names = T, booktabs = T)
```


###Weight of each category in the fishery ($W_{i,t}$; e.g., K, L, ...) 

$$W_{i,t} = (P_{i,t}*Q_{i,t})/V_{t}$$

where: 

 - $W_{i,t}$ is the weight of the category (i) for each year (t) in the fishery
 

```{r, echo  = FALSE}
tempW<-data.frame(data = rep_len(x = NA, length.out = nrow(temp)))
for (c in 1:length(VColumns)) {
  
  #for renaming the columns
    NameBase<-substr(start = 2, 
                   stop = nchar(names(temp)[QColumns[c]]), 
                   x = names(temp)[QColumns[c]]) 
    
  V<-temp[,grep(pattern = paste0("V", NameBaseTotal), x = names(temp))]
  V0<-temp[,names(temp) %in% paste0("V", NameBase)] #to make sure its the same column
  tempW[,c]<-V0/V
  names(tempW)[c]<-paste0("W", NameBase ) #name the column
}

tempW<-data.frame(tempW)
temp<-cbind.data.frame(temp, tempW)
```

```{r, echo  = FALSE}
rownames(tempW)<-rownames(temp)
tempW %>%
    knitr::kable(row.names = T, booktabs = T)
```

###Price Changes for each category ($PC_{i,t}$ aka $\Delta ln(P_{i,t})$; e.g., K, L, ...)

$$PC_{i,t} = ln(\frac{P_{i,t}}{P_{i,t-1}}) = \sum_{s=1}^n([\frac{W_{i,t} + W_{i,t-1}}{2}] * [ln(\frac{P_{i,t}}{P_{i,t-1}}]) = \sum_{s=1}^n([\frac{W_{i,t} + W_{i,t-1}}{2}] * [ln(P_{i,t}) - ln(P_{i,t-1})]) $$

Where:

 - category's (i) Price for each category (i), for each year (t) = $P_{i,t}$

 - category's (i) Weight for each category (i), for each year (t) = $W_{i,t}$

Which can be adapted to this function/macro:

```{r, echo  = TRUE}
#A function to caluclate the price change
print(pricechange)
```

Now put it into practice for the total dataset:

```{r, echo  = TRUE}
#Find which columns in this table are price and revenue share columns
tempPC<-data.frame(data = rep_len(x = NA, length.out = nrow(temp)))
for (c in 1:length(PColumns)){
  #For nameing columns
    NameBase<-substr(start = 2, 
                   stop = nchar(names(temp)[QColumns[c]]), 
                   x = names(temp)[QColumns[c]]) 
  
  # Calculate
  P0<-temp[, names(temp) %in% paste0("P", NameBase)]
  R0<-temp[, names(temp) %in% paste0("W", NameBase)] #to make sure its the same column
  tempPC[,c]<-pricechange(R0, P0)
  names(tempPC)[c]<-paste0("PC", NameBase ) #name the column
}

temp<-cbind.data.frame(temp, tempPC)
```

For reference, here are the Price Changes for each species ($PC_{s,i,t}$):

```{r, echo  = FALSE}
rownames(tempPC)<-rownames(temp)
tempPC %>%
    knitr::kable(row.names = T, booktabs = T)
```


###Summed Price Change for the fishery ($PC_{t}$)

$$PC_{t} = \sum_{i=1}^{m} PC_{i,t}$$

Where:

 - category's (i) Price Change of the fishery, for each year (t) = $PC_{t}$
 
```{r, echo  = TRUE}
temp[ncol(temp)+1]<-rowSums(tempPC, na.rm = T)
names(temp)[ncol(temp)]<-paste0("PC", NameBaseTotal)
```

```{r, echo  = FALSE}
temp0<-cbind.data.frame("Other..." = rep_len(x = "...", length.out = nrow(temp)), 
                 temp[,(ncol(temp)-4):ncol(temp)])
temp0 %>%
    knitr::kable(row.names = T, booktabs = T)
```
 
###Price for the entire commercial fishery ($P_t$)

$$P_t = P_{t-1}*[1+ln(\frac{P_{i,t}}{P_{i,t-1}})] = P_{t-1}*[1-PC_{t}]$$

Which is represented using this function:
```{r, echo  = TRUE}
#Note that the first row of this column is = 1
tempP<-c(1, rep_len(x = NA, length.out = nrow(temp)-1))

PC0<-temp[,paste0("PC", NameBaseTotal)] #this is equal to ln(P_it/P_it-1)

  #Since the first row is defined, we need to start at the second row
for (t in 2:length(tempP)){
    tempP[t]<-tempP[t-1]*(1+PC0[t])
}
  
temp[,ncol(temp)+1]<-tempP
names(temp)[ncol(temp)]<-paste0("P", NameBaseTotal)
```

```{r, echo  = FALSE}
temp0<-cbind.data.frame("Other..." = rep_len(x = "...", length.out = nrow(temp)), 
                 temp[,(ncol(temp)-4):ncol(temp)])
temp0 %>%
    knitr::kable(row.names = T, booktabs = T)
```

###Price Index for the entire commercial fishery ($PI_t$)

$$PI_{t} = \frac{P_{t}}{P_{t=baseyr}}$$

In this example, we'll decide that the base year is 2010, for whatever reason. Notice that the $PI_{i,t=2007} = 1$ 

```{r, echo  = FALSE}
baseyr<-2007
temp[,ncol(temp)+1]<-temp[,paste0("P", NameBaseTotal)]/temp[rownames(temp) %in% baseyr,paste0("P", NameBaseTotal)]
names(temp)[ncol(temp)]<-paste0("PI", NameBaseTotal)
```

```{r, echo  = FALSE}
temp0<-cbind.data.frame("Other..." = rep_len(x = "...", length.out = nrow(temp)), 
                 temp[,(ncol(temp)-4):ncol(temp)])
temp0 %>%
    knitr::kable(row.names = T, booktabs = T)
```

### Total Implicit Quantity Input for the entire commercial fishery ($Q_t = Y_t$)
To get quantity estimates for total output using total value of landings divided by price index as follow: $Y=Q=V/I$ 

$$Q_{t}=V_{t}/PI_{t}$$

```{r, echo  = TRUE}
temp[,ncol(temp)+1]<-temp[,paste0("V", NameBaseTotal)]/temp[,paste0("PI", NameBaseTotal)]
names(temp)[ncol(temp)]<-paste0("Q", NameBaseTotal)
```

```{r, echo  = FALSE}
temp0<-cbind.data.frame("Other..." = rep_len(x = "...", length.out = nrow(temp)), 
                 temp[,(ncol(temp)-4):ncol(temp)])
temp0 %>%
    knitr::kable(row.names = T, booktabs = T)
```

### Total Implicit Quantity/Output Index

$$QI_t = Q_t/Q_{t=baseyr}$$

Where:

 - $QI$ is the sum of Q after these equations
 
```{r, echo  = TRUE}
    temp$QI0_0Total<-temp$Q0_0Total/temp$Q0_0Total[rownames(temp) %in% baseyr]
```

```{r, echo  = FALSE}
temp0<-cbind.data.frame("Other..." = rep_len(x = "...", length.out = nrow(temp)), 
                 temp[,(ncol(temp)-4):ncol(temp)])
temp0 %>%
    knitr::kable(row.names = T, booktabs = T)
```

### Sum Total Implicit Quantity/Output Index (Optional)

$$QEI_t = QE_t/QE_{t=baseyr}$$

Where:

 - $QE$ is the sum of Q before these equations
 
 - $QEI$ is the index of the sum of Q before these equations

```{r, echo  = TRUE}
temp$QEI0_0Total<-temp$QE0_0Total/temp$QE0_0Total[rownames(temp) %in% baseyr]
```

```{r, echo  = FALSE}
temp0<-cbind.data.frame("Other..." = rep_len(x = "...", length.out = nrow(temp)), 
                 temp[,(ncol(temp)-4):ncol(temp)])
temp0 %>%
    knitr::kable(row.names = T, booktabs = T)
```

### Solve Output portion of the equation for the Input Changes: 

$$QC_t = \sum_{i=1}^n((\frac{R_{it} + R_{it-1}}{2}) * ln(\frac{Q_{it}}{Q_{it-1}}))$$

```{r, echo  = TRUE}
#Find which columns in this table are price and revenue share columns
tempQC<-data.frame(data = rep_len(x = NA, length.out = nrow(temp)))
for (c in 1:length(PColumns)){
  #For nameing columns
    NameBase<-substr(start = 2, 
                   stop = nchar(names(temp)[QColumns[c]]), 
                   x = names(temp)[QColumns[c]]) 
  
  # Calculate
  P0<-temp[, names(temp) %in% paste0("Q", NameBase)]
  R0<-temp[, names(temp) %in% paste0("W", NameBase)] #to make sure its the same column
  tempQC[,c]<-pricechange(R0, P0)
  names(tempQC)[c]<-paste0("QC", NameBase ) #name the column
}

temp<-cbind.data.frame(temp, tempQC)
```

For reference, here are the Price Changes for each species ($PC_{s,i,t}$):

```{r, echo  = FALSE}
rownames(tempQC)<-rownames(temp)
tempQC %>%
    knitr::kable(row.names = T, booktabs = T)
```


###Summed Price Change for the fishery ($PC_{t}$)

$$QC_{t} = \sum_{i=1}^{m} QC_{i,t}$$

Where:

 - category's (i) Price Change of the fishery, for each year (t) = $PC_{t}$
 
```{r, echo  = TRUE}
temp[ncol(temp)+1]<-rowSums(tempQC, na.rm = T)
names(temp)[ncol(temp)]<-paste0("QC", NameBaseTotal)
```

```{r, echo  = FALSE}
temp0<-cbind.data.frame("Other..." = rep_len(x = "...", length.out = nrow(temp)), 
                 temp[,(ncol(temp)-4):ncol(temp)])
temp0 %>%
    knitr::kable(row.names = T, booktabs = T)
```

```{r, echo  = FALSE}
temp[names(temp) %in% c("Q0_0Total", "QI0_0Total", "QC0_0Total")] %>%
    knitr::kable(row.names = T, booktabs = T)
```

### Graph 1
```{r, echo  = TRUE}
#A function I made to plot this pretty in ggplot2
plot1line(temp, PI = temp$PI0_0Total, 
            NOAALightBlue, NOAADarkBlue, NOAADarkGrey)
```


### Graph 2
```{r, echo  = TRUE}

temp0<-temp
temp0$Year<-rownames(temp0)

tempA<-data.frame(temp0[,names(temp0) %in% c("Year", "QI0_0Total")])
names(tempA)<-c("Index", "Year")
tempA$group<-"QI_Total"
tempA$col<-NOAALightBlue

tempB<-data.frame(temp0[,names(temp0) %in% c("Year", "QEI0_0Total")])
names(tempB)<-c("Index", "Year")
tempB$group<-"QEI_Total"
tempB$col<-NOAADarkBlue

temp0<-rbind.data.frame(tempA, tempB)
rownames(temp0)<-NULL
temp0$col<-as.factor(temp0$col)

#A function I made to plot this pretty in ggplot2
plot2line(temp0, Year = temp0$Year, Index=temp0$Index, col = temp0$col, group = temp0$group, 
                    NOAALightBlue, NOAADarkBlue, NOAADarkGrey)
```

## Do same analysis via a function!

Now that we know the method, we can simplify most of it into a function and do this whole analysis in 4 easy steps: 

 - A. Import and Edit data
 
 - B. Enter base year
 
 - C. Run the function
 
 - D. Obtain the implicit quantity estimates

### Function to calculate the Implicit Quanity Input at Fishery Level
```{r, echo = TRUE}
print(ImplicitQuantityInput)
```

### A. Import and Edit data
```{r, echo = TRUE, warning = FALSE}
temp<-read.csv(file = paste0(dir.data, "Tornqvist Index-Calculations_InputEx.csv"))
rownames(temp)<-temp$year
temp$year<-NULL

temp.q<-temp[,grepl(pattern = "Q", x = names(temp))]
temp$QE0_0Total<-rowSums(temp.q, na.rm = T)

temp<-orgional.data<-cbind.data.frame(temp)
```

 
### B. Enter base year
```{r, echo = TRUE, warning = FALSE}
 baseyr<-2007
```
 
### C. Run the function
```{r, echo = TRUE, warning = FALSE}
temp<-ImplicitQuantityInput(temp, baseyr, calcQEI = T)
```

### D. Obtain the implicit quantity estimates
```{r, echo = FALSE, warning = FALSE}
write.csv(x = temp, file = paste0(dir.docu, "Example_Input.csv"))

temp0<-temp[, grepl(pattern = "0Total", x = names(temp))]

temp0 %>%
    knitr::kable(row.names = T, booktabs = T)
```

### Graph 1
For comparison, let's recreate those graphs to make sure we are getting the same output:
```{r, echo  = TRUE}
#A function I made to plot this pretty in ggplot2
plot1line(temp, PI = temp$PI0_0Total, 
            NOAALightBlue, NOAADarkBlue, NOAADarkGrey)
```

### Graph 2
For comparison, let's recreate those graphs to make sure we are getting the same output:
```{r, echo  = TRUE}

temp0<-temp
temp0$Year<-rownames(temp0)

tempA<-data.frame(temp0[,names(temp0) %in% c("Year", "QI0_0Total")])
names(tempA)<-c("Index", "Year")
tempA$group<-"QI_Total"
tempA$col<-NOAALightBlue

tempB<-data.frame(temp0[,names(temp0) %in% c("Year", "QEI0_0Total")])
names(tempB)<-c("Index", "Year")
tempB$group<-"QEI_Total"
tempB$col<-NOAADarkBlue

temp0<-rbind.data.frame(tempA, tempB)
rownames(temp0)<-NULL
temp0$col<-as.factor(temp0$col)

plot2line(temp0, Year = temp0$Year, Index=temp0$Index, col = temp0$col, group = temp0$group, 
                    NOAALightBlue, NOAADarkBlue, NOAADarkGrey)
```

-------

#Use examples to do the whole $TFP$ Equation

## A. Import and Edit data

Output
``` {r, echo  = TRUE} 
temp<-read.csv(file = paste0(dir.data, "Tornqvist Index-Calculations_OutputEx.csv"))
rownames(temp)<-temp$year
temp$year<-NULL

temp.q<-temp[,grepl(pattern = "Q", x = names(temp))]
temp.q$QE0_0Total<-rowSums(temp.q, na.rm = T)
temp.q$QE1_0Finfish<-rowSums(temp.q[,grepl(x = names(temp.q), pattern = "Q1") ], na.rm = T)
temp.q$QE2_0Shellfish<-rowSums(temp.q[,grepl(x = names(temp.q), pattern = "Q2") ], na.rm = T)

temp.v<-temp[,grepl(pattern = "V", x = names(temp))]
temp.v$V0_0Total<-rowSums(temp.v, na.rm = T)
temp.v$V1_0Finfish<-rowSums(temp.v[,grepl(x = names(temp.v), pattern = "V1") ], na.rm = T)
temp.v$V2_0Shellfish<-rowSums(temp.v[,grepl(x = names(temp.v), pattern = "V2") ], na.rm = T)

temp.output<-cbind.data.frame(temp.q, temp.v)
```

Input:
``` {r, echo  = TRUE} 
temp<-read.csv(file = paste0(dir.data, "Tornqvist Index-Calculations_InputEx.csv"))
rownames(temp)<-temp$year
temp$year<-NULL

temp.q<-temp[,grepl(pattern = "Q", x = names(temp))]
temp$QE0_0Total<-rowSums(temp.q, na.rm = T)

temp.input<-orgional.data<-cbind.data.frame(temp)
```

## B. Enter base year

``` {r, echo  = TRUE} 
baseyr<-2007
```

## C. Run the function


###Function Method 1 to Calcilate the TFP

$$TFP_t = \frac{Y_t}{X_t}$$

$$TFPCR_t = ln(TFP_{t}/TFP_{t-1})$$

where

 - $TFPCR_t$ is the change rate of the TFP over time t

``` {r, echo  = TRUE} 
print(TFP_ChangeRate_Method1)
```

```{r, echo = FALSE}
TFP1_CR<-TFP_ChangeRate_Method1(temp.output, temp.input, baseyr, calcQEI = T, PercentMissingThreshold)
```

``` {r, echo  = FALSE} 
NumberOfSpecies<-numbers0(x = c(0, strsplit(x = 
                                                strsplit(x = names(TFP1_CR)[3], 
                                                         split = "_")[[1]][2], 
                                              split = "[a-zA-Z]")[[1]][1]))[1]

temp<-TFP1_CR[, c(grep(pattern = paste0("Y",NumberOfSpecies,".*Total"), x = names(TFP1_CR)) , 
                grep(pattern = paste0("X",NumberOfSpecies,".*Total"), x = names(TFP1_CR)) ,
                grep(pattern = "TFP", x = names(TFP1_CR)))]
names(temp)<-c("Y_Total", "X_Total", "TFP", "TFP_CR")
temp %>%
    knitr::kable(row.names = T, booktabs = T)
```

### Function Method 2 to Calcilate the TFP

$$ln(TFP_t/TFP_{t-1}) = \sum_{i=1}^n((\frac{R_{i,t} + R_{i,t-1}}{2}) * ln(\frac{Y_{i,t}}{Y_{i,t-1}}))) - \sum_{j=1}^m((\frac{W_{j,t} + W_{j,t-1}}{2}) * ln(\frac{X_{j,t}}{X_{j,t-1}})))$$

``` {r, echo  = TRUE} 
print(TFP_ChangeRate_Method2)
```

``` {r, echo  = TRUE} 
TFP2_CR<-TFP_ChangeRate_Method2(temp.output, temp.input, baseyr, calcQEI = T, PercentMissingThreshold)
```
 
###Method 1 using $YE$ (summed, not calculated, output) for comparison
```{r, echo = TRUE}
  NumberOfSpecies<-numbers0(x = c(0, strsplit(x = 
                                                strsplit(x = names(temp)[1], 
                                                         split = "_")[[1]][2], 
                                              split = "[a-zA-Z]")[[1]][1]))[1]

  #OUTPUT
  temp00<-ImplicitQuantityOutput(temp.output, baseyr, calcQEI = T, PercentMissingThreshold)
temp<-temp00[[1]]
warnings.list0<-temp00[[2]]
figures.list0<-temp00[[3]]

  names(temp)<-paste0(gsub(pattern = "Q", replacement = "Y", 
                           x = substr(x = names(temp), start = 1, stop = 1)), 
                      substr(x = names(temp), start = 2, stop = nchar(names(temp))))
  temp.output1<-temp
  
  
  #input
  temp<-ImplicitQuantityInput(temp.input, baseyr, calcQEI = T)
  names(temp)<-paste0(gsub(pattern = "Q", replacement = "X", 
                           x = substr(x = names(temp), start = 1, stop = 1)), 
                      substr(x = names(temp), start = 2, stop = nchar(names(temp))))
  temp.input1<-temp

  #Calculate
  TFP1<-temp.output1[,grep(pattern = paste0("YE",NumberOfSpecies,".*Total"), x = names(temp.output1))] / 
    temp.input1[,grep(pattern = paste0("X",NumberOfSpecies,".*Total"), x = names(temp.input1))] 
  
  
  TFP1E_CR<-rep_len(x = 0, length.out = length(TFP1))
  for (i in 2:length(TFP1)) {
    TFP1E_CR[i] <- ln(TFP1[i]/TFP1[i-1])
  }
  
  TFP1E_CR<-data.frame(TFP1E_CR)
  names(TFP1E_CR)<-c("TFP1_CR")
  rownames(TFP1E_CR)<-rownames(temp.output1)
```

```{r, echo = FALSE}
TFP1E_CR %>%
    knitr::kable(row.names = T, booktabs = T)
```

###Method 2 using $YE$ (summed, not calculated, output) for comparison

```{r, echo = TRUE}
  #OUTPUT

  temp00<-ImplicitQuantityOutput(temp.output, baseyr, calcQEI = T, PercentMissingThreshold)
  temp<-temp00[[1]]
  warnings.list0<-temp00[[2]]
  figures.list0<-temp00[[3]]

  names(temp)<-paste0(gsub(pattern = "Q", replacement = "Y", 
                           x = substr(x = names(temp), start = 1, stop = 1)), 
                      substr(x = names(temp), start = 2, stop = nchar(names(temp))))
  temp.output1<-temp
  
    temp$YEC0_0Total<-rowSums(cbind(pricechange(R0 = temp$R1_0Finfish, P0 = temp$YE1_0Finfish), 
                            pricechange(R0 = temp$R2_0Shellfish, P0 = temp$YE2_0Shellfish)), 
                       na.rm = T)
  
  
  #input
  temp<-ImplicitQuantityInput(temp.input, baseyr, calcQEI = T)
  names(temp)<-paste0(gsub(pattern = "Q", replacement = "X", 
                           x = substr(x = names(temp), start = 1, stop = 1)), 
                      substr(x = names(temp), start = 2, stop = nchar(names(temp))))
  temp.input1<-temp
  

  
  
  
  TFP <- temp.output1[,grep(pattern = "YC.*Total", x = names(temp.output1))] - 
    temp.input1[,grep(pattern = "XC.*Total", x = names(temp.input1))]
  
  TFP2E_CR<-data.frame(TFP)
  names(TFP2E_CR)<-"TFP2_CR"
  rownames(TFP2E_CR)<-rownames(temp.output1)
```

```{r, echo = TRUE}
TFP2E_CR %>%
    knitr::kable(row.names = T, booktabs = T)
```

## D. Obtain the implicit quantity estimates

```{r, echo  = TRUE}
## Graph 1
# For comparison, let's recreate those graphs to make sure we are getting the same output:

#A function I made to plot this pretty in ggplot2
# TFP<-cbind.data.frame(TFP1_CR, TFP2_CR)
# plot2line(temp0 = TFP, PI = TFP$TFP1, 
            # NOAALightBlue, NOAADarkBlue, NOAADarkGrey)
```

## Graph 2: Compare methods
``` {r, echol = FALSE}
TFP$TFP1<-NULL

TFP1_CR$Year<-rownames(TFP1_CR)
tempA<-data.frame(TFP1_CR[,names(TFP1_CR) %in% c("Year", "TFP1_CR")])
names(tempA)<-c("Index", "Year")
tempA$group<-"M1 with Calc. TFP"
tempA$col<-NOAALightBlue

TFP2_CR$Year<-rownames(TFP2_CR)
tempB<-data.frame(TFP2_CR[,names(TFP2_CR) %in% c("Year", "TFP2_CR")])
names(tempB)<-c("Index", "Year")
tempB$group<-"M2 with Calc. TFP"
tempB$col<-NOAADarkBlue

TFP1E_CR$Year<-rownames(TFP1E_CR)
tempC<-data.frame(TFP1E_CR[,names(TFP1E_CR) %in% c("Year", "TFP1_CR")])
names(tempC)<-c("Index", "Year")
tempC$group<-"M1 with Sum. TFP"
tempC$col<-"#a66600"

TFP2E_CR$Year<-rownames(TFP2E_CR)
tempD<-data.frame(TFP2E_CR[,names(TFP2E_CR) %in% c("Year", "TFP2_CR")])
names(tempD)<-c("Index", "Year")
tempD$group<-"M2 with Sum. TFP"
tempD$col<-"#a60000"

temp0<-rbind.data.frame(tempA, tempB)#, tempC, tempD)
rownames(temp0)<-NULL
temp0$col<-as.factor(temp0$col)

plot2line(temp0, Year = temp0$Year, Index=temp0$Index, col = temp0$col, group = temp0$group, 
                    NOAALightBlue, NOAADarkBlue, NOAADarkGrey)

```

