---
title: ""
author: ""
date: ""
output: 
  word_document:
    df_print: kable
    reference_docx: word-styles-reference.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
designflowin<-FALSE
```

## Productivity Output Index

```{r p1}
minyr<-2009
maxyr<-2018

dir.in<-dirname(getwd())
dir.data<-dir.rawdata<-paste0(dir.in, "/data/")
dir.output<-paste0(dir.in, "/output/")
dir.out<-paste0(dir.output, "ProductivityIndex_", Sys.Date(), "/")
dir.scripts<-paste0(dir.in, "/rscripts/")
dir.analyses<-paste0(dir.out, "/analyses/")
ProdI.Report<-paste0(dir.scripts, "ProductivityIndex_Report.rmd")

# aaa<-unlist(unique(lapply(fold0, `[[`, 1)))

library(devtools)
devtools::install_github("emilyhmarkowitz/FishEconProdOutput", dependencies = TRUE)
library(FishEconProdOutput)

### SOURCE FILES AND DATA #####
#Load data for this section
#Functions specific to this section
ProdI.Funct<-paste0(dir.scripts, "ProductivityIndex_Functions.R")
source(ProdI.Funct)

aa<-list.files(path = paste0(dir.analyses), 
                           pattern = paste0(minyr, "To", maxyr, "_FS"), 
                           full.names = TRUE)

bb<-list.files(path = paste0(aa, "/outputtables/"), full.names = TRUE, pattern = "000_All")




```


#### Table [1]. Regional Landing Values, `r minyr`-`r maxyr` (Implicit Quantity in `r maxyr` $ Million)

```{r p3}

a<-data.frame(Year = minyr:maxyr)
for (i in 2:length(reg.order)){
  temp<-read.xlsx(file = bb[grep(pattern = "_FinalOutput", x = bb)], sheetName = reg.order[i])
  a<-cbind.data.frame(a, temp[,names(temp) %in% "QI_Total"])
}
names(a)<-c("Year", reg.order[2:length(reg.order)])
a$Northeast<-NULL
names(a)<-gsub(pattern = " \\(Hawai`i\\)", replacement = "", x = names(a))

a[,2:ncol(a)]<-round(x = a[,2:ncol(a)], digits = 2)

if (designflowin %in% F){
  # print(a %>%
  #   knitr::kable(row.names = T, booktabs = T))
  
  
  a %>% 
  # tibble::rownames_to_column() %>% 
  flextable() %>%
  set_header_labels(rowname = "") %>% 
  # add_header_row(values = c("", "Group 1", "Group 2"), 
  #                colwidths = c(1, 2, 2)) %>% 
   theme_box()# %>% autofit()
  
}
```


#### Table [2]. Regional Price Index, `r minyr`-`r maxyr` (`r maxyr` = 1)

```{r p4}

a<-data.frame(Year = minyr:maxyr)
for (i in 2:length(reg.order)){
  temp<-read.xlsx(file = bb[grep(pattern = "_FinalOutput", x = bb)], sheetName = reg.order[i])
  a<-cbind.data.frame(a, temp[,names(temp) %in% "PI_Total"])
}
names(a)<-c("Year", reg.order[2:length(reg.order)])

a$Northeast<-NULL
names(a)<-gsub(pattern = " \\(Hawai`i\\)", replacement = "", x = names(a))

a[,2:ncol(a)]<-round(x = a[,2:ncol(a)], digits = 2)

if (designflowin %in% F){
  # print(a %>%
  #   knitr::kable(row.names = T, booktabs = T))
  
  a %>% 
  # tibble::rownames_to_column() %>% 
  flextable() %>%
  set_header_labels(rowname = "") %>% 
  # add_header_row(values = c("", "Group 1", "Group 2"), 
  #                colwidths = c(1, 2, 2)) %>% 
   theme_box()# %>% autofit()
  
}
```


#### Table [3]. National Landing Values (Implicit Quantity in `r maxyr` $ Million) and Price Index, (`r maxyr` = 1), `r minyr`-`r maxyr` 

```{r p5}

keydatatable<-function(Date0, yr, maxyr, folderpattern, dir.output) {
  outputrun<-list.files(path = dir.output, pattern = as.character(Date0), full.names = TRUE)
  a<-list.files(path = (list.files(path = paste0(outputrun, "/analyses/"), full.names = TRUE, pattern = paste0(yr, "To", maxyr, "_", folderpattern))),
                     pattern = "outputtables", full.names = TRUE, ignore.case = TRUE)
  b<-a[(grepl(pattern =paste0(yr, "To"), x = a))]
  b<-list.files(path = b, pattern = "_US_", full.names = TRUE)
  b<-b[grep(pattern = "_Review", x = b)]

  # b<-load(paste0(a, "/AllFigures.rdata"))
  a<-read.csv(file = b)
  rownames(a)<-a$X
  a$X<-NULL

  a<-a[,(grepl(pattern = "PI",x = names(a)) |
          grepl(pattern = "Q[0-9]+_",x = names(a)) |
          grepl(pattern = "Q_Total",x = names(a)) #|
          # grepl(pattern = "QI",x = names(a))
         )]

  aa<-cbind.data.frame(data.frame(a[,grepl(pattern = "Total", x = names(a))]),
                      data.frame(a[,!(grepl(pattern = "Total", x = names(a)))]))
  names(aa)<-c(names(a)[grepl(pattern = "Total", x = names(a))],
              names(a)[!(grepl(pattern = "Total", x = names(a)))])
  a<-aa
  groups<-unlist(lapply(strsplit(split = "_", x = names(a)), `[[`, 2))
  names(a)<-gsub(pattern = "[0-9]+", replacement = "", x = names(a))
  names(a)<-gsub(pattern = "_[a-zA-Z]+", replacement = "", x = names(a))

  a[,(names(a) == "Q")]<-a[,(names(a) == "Q")]/1e6

  if (sum(names(a) == "PI")>0) {
  for (i in 1:length(which(names(a) == "PI"))){
    a[,which(names(a) == "PI")[i]]<-a[,which(names(a) == "PI")[i]]/a[1,which(names(a) == "PI")[i]]
  }
  }
  #   for (i in 1:length(which(names(a) == "QI"))){
  #   a[,which(names(a) == "QI")[i]]<-a[,which(names(a) == "QI")[i]]/a[1,which(names(a) == "QI")[i]]
  # }

  g<-t(data.frame(table(groups)))
  g<-g[,match(table = g[1,], x = unique(groups))]


a %>%
  tibble::rownames_to_column() %>%
  flextable() %>%
  set_header_labels(rowname = "") %>%
  add_header_row(values = c("", g[1,]),
                 colwidths = c(1, as.numeric(g[2,]))) %>%
   theme_box() %>% autofit()
}


if (designflowin %in% F){
keydatatable(Date0 = Sys.Date(), yr = minyr, maxyr = maxyr, 
             folderpattern = "", dir.output)

}
```

#### Graph [1]. National Landing Values (Implicit Quantity in [`r minyr`] $ Million), `r minyr`-`r maxyr` 

```{r p6}

a<-data.frame(Year = minyr:maxyr)

temp<-read.xlsx(file = bb[grep(pattern = "_Review", x = bb)], sheetName = reg.order[1])

Q<-cbind.data.frame(temp$Q_Total,
  temp[,grep(x = names(temp), pattern = "Q[0-9]+_")])
Q<-round(x = Q/1e6, digits = 2)

a<-cbind.data.frame(a, Q)

names(a)<-gsub(pattern = "[0-9]+", replacement = "", x = names(a))
names(a)<-gsub(pattern = "temp\\$", replacement = "", x = names(a))
names(a)<-gsub(pattern = "Q_", replacement = "", x = names(a))

a<-a[,match(table = names(a),
            x = c("Year","Total",
                  "Finfish", "Shellfish"))]


a0<-a
a <- gather(a0, Category, val, names(a0)[-1], factor_key=TRUE)

a$cat<-a$Category

temp0<-a


g<-plotnlines(dat = temp0, 
              titleyaxis = paste0("Implicit Quantity in [", minyr,"] $ Million"), 
              title0 = "")

if (designflowin %in% F){
  g
} 

# counter<-funct_counter(counter)
# ggsave(g,
#        filename = paste0(dir.figures, filename0, "_", counter, "_G4_Figure.pdf"),
#        width = 4, height = 4)

```

#### Graph [2]. Total Quantity Index for Each Region (`r minyr` = 1), `r minyr`-`r maxyr`

```{r p7}

a<-data.frame(Year = minyr:maxyr)
for (i in 2:length(reg.order)){
  temp<-read.xlsx(file = bb[grep(pattern = "_FinalOutput", x = bb)], sheetName = reg.order[i])
  a<-cbind.data.frame(a, temp[,names(temp) %in% "Q_Total"])
}
names(a)<-c("Year", reg.order[2:length(reg.order)])

a0<-a
a <- gather(a0, Category, val, names(a0)[-1], factor_key=TRUE)

a$cat<-a$Category

temp0<-a

g<-plotnlines(dat = temp0, titleyaxis = paste0("Quantity Index (", minyr," = 1)"), title0 = "")

if (designflowin %in% F){
  g
} 

# counter<-funct_counter(counter)
# ggsave(g,
#        filename = paste0(dir.figures, filename0, "_", counter, "_G4_Figure.pdf"),
#        width = 4, height = 4)

```


