---
title: "Measuring Output for U.S. Commercial Fisheries — From Theory to Practice"
author: 'Emily Markowitz^1^ (Emily.Markowitz@noaa.gov) Sun Ling Wang^2^ (Sun-Ling.Wang@noaa.gov) \n\n ^1^Contractor, ECS Federal in support of NOAA Fisheries Office of Science and Technology Economics & Social Analysis Division \n\n ^2^On detail with the NOAA Fisheries Office of Science and Technology Economics & Social Analysis Division \n\n >*The views expressed are those of the author and should not be attributed to the NOAA, ECS or ERS'
date: "`r Sys.Date()`"
output: 
  powerpoint_presentation:
    reference_doc: NOAAFisheriesPowerPointTemplate.pptx
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
#   dev = "svg",
  fig.width = 12,
  fig.height = 7
  # fig.retina = 3
  )

print4plots<-function(plotlist, datadl, title00, legends = c(T,T,T,T), titles = c(F,F,F,F)){

  b0<-list()
  for (i in 1:length(plotlist)){
    
    b<-plotlist[i][[1]]
    b<-b+
      geom_line(aes(group = cat), size = 2) +
      theme_classic(base_size = 20) 
    if(legends[i] %in% F) {
      b<-b + theme(legend.position = "none")
    } else {
      b<-b + theme(legend.title = element_blank())
    }
    if(titles[i] %in% F) {
      b<-b + ggtitle("")
    }
    b0<-c(b0, list(b))
    }
    
  
  b<-plotlist
  layout <- (b0[1][[1]] + b0[2][[1]]) / (b0[3][[1]] + b0[4][[1]])
  
  title0<-strsplit(split = "_", x = names(b)[1])[[1]][-c(1,2)]
  title0<-title0[-length(title0)]
  title0<-gsub(pattern = "byr", replacement = "base yr = ", x = title0)
  title0<-paste(title0, collapse = " ")
  title0<-gsub(pattern = " P ", replacement = " Price Method ", x = title0)
  title0<-gsub(pattern = " Q ", replacement = " Quantity Method ", x = title0)
  
  layout +
    plot_annotation(
    title = title00, 
    subtitle = "",
    caption = paste0(title0, "\n Data downloaded from FOSS ", datadl, ". "),
    theme = theme(plot.title = element_text(size = 20, hjust = 0.5, face = "bold"))
    )
}


xunits<-function(temp00, combine=T) {
  
  temp00<-sum(as.numeric(temp00))
  sigfig<-format(temp00, digits = 3, scientific = TRUE)
  sigfig0<-as.numeric(substr(x = sigfig, start = (nchar(sigfig)-1), stop = nchar(sigfig)))
  
  if (sigfig0<=5) {
    # if (sigfig0<4) {
    unit<-""
    x<-format(x = temp00, big.mark = ",", digits = 0, scientific = F)
    # } else if (sigfig0>=4 & sigfig0<6) {
    #   unit<-" thousand"
    # x<-round(temp00/1e3, digits = 1)
    # } else if (sigfig0==5) {
    #   unit<-" thousand"
    #   x<-round(temp00/1e3, digits = 0)
  } else if (sigfig0>=6 & sigfig0<9) {
    unit<-" million"
    x<-round(temp00/1e6, digits = 1)
  } else if (sigfig0>=9 & sigfig0<12) {
    unit<-" billion"
    x<-round(temp00/1e9, digits = 1)
  } else if (sigfig0>=12) {
    unit<-" trillion"
    x<-round(temp00/1e12, digits = 1)
  }
  
  out<-ifelse(combine==T, paste0(x, unit), list(x, unit))
  
  return(out)
}

plotkeyfig<-function(yr, place, folderpattern, 
                      plotpartnames, plotyaxis = c(NA, NA, NA, NA)){

  outputrun<-list.files(path = dir.output, pattern = as.character(Date0), full.names = TRUE)
  a<-list.files(path = (list.files(path = paste0(outputrun, "/analyses/"), full.names = TRUE, pattern = folderpattern)), 
                     pattern = "figures", full.names = TRUE, ignore.case = TRUE)
  b<-a[(grepl(pattern =paste0(yr, "To"), x = a))]
  # b<-load(paste0(a, "/AllFigures.rdata"))
  
  load(file = paste0(b, "/AllFigures.rdata"))
  
  if (sum(grepl(pattern = place, x = names(figures.list), ignore.case = T)) != 0) {
    
    for (i in 1:length(plotpartnames)){
  c1<-figures.list[grepl(pattern = plotpartnames[1], x = names(figures.list), ignore.case = T) & 
                    grepl(pattern = place, x = names(figures.list), ignore.case = T)]
  if (plotpartnames[i] %in% c("QI-Line", "PI-Line")){
  aa<-c1[[1]]$data
    for ( i in 1:length(unique(aa$cat))){
      aaa<-aa[aa$cat %in% unique(aa$cat)[i],]
      aaa$val<-aaa$val/aaa$val[aaa$Year %in% min(aaa$Year)]
      aa[aa$cat %in% unique(aa$cat)[i],]<-aaa
    }
    c1[[1]]$data<-aa
  }
  if (!(is.na(plotyaxis[i]))) {
      c1[[1]]$labels$y<-plotyaxis[i]
  }
  assign(value = c1[[1]], x = paste0("c", i))
}

  
  p<-print4plots(plotlist = c(c1, c2, c3, c4), 
                     datadl = datadl, title00 = "", 
                     legends = c(F,T,F,F))
  } else {
    
    title0<-strsplit(split = "/", x = b)
    title0<-title0[[1]][length(title0[[1]])-1]
    
    title0<-strsplit(split = "_", x = title0)[[1]]
    # title0<-title0[-length(title0)]
    title0<-gsub(pattern = "To", replacement = "-", x = title0)
    title0<-gsub(pattern = "byr", replacement = "base yr = ", x = title0)
    title0<-paste(title0, collapse = " ")
    title0<-gsub(pattern = " P ", replacement = " Price Method ", x = title0)
    title0<-gsub(pattern = " Q ", replacement = " Quantity Method ", x = title0)
    
    p <- ggplot(dat = data.frame(x=1,y=1), aes(x, y, 
                                               label = "We could not perform this analysis on this region")) + 
      geom_text() + 
      theme(panel.background = element_blank(), 
            axis.title = element_blank(), 
            axis.text = element_blank(), 
            axis.ticks = element_blank()) + 
      ggtitle(title0)
    
  }
  

  return(p)
}

  
speciestable<-function(Date0, yr, maxyr, folderpattern, dir.output){
  outputrun<-list.files(path = dir.output, pattern = as.character(Date0), full.names = TRUE)
  a<-list.files(path = (list.files(path = paste0(outputrun, "/analyses/"), full.names = TRUE, pattern = paste0(yr, "To", maxyr, "_", folderpattern))), 
                     pattern = "outputtables", full.names = TRUE, ignore.case = TRUE)
  b<-a[(grepl(pattern =paste0(yr, "To"), x = a))]
  b<-list.files(path = b, pattern = "_All_", full.names = TRUE)
  b<-b[grep(pattern = "_Species", x = b)]
  
  # b<-load(paste0(a, "/AllFigures.rdata"))
  a<-read.csv(file = b)

  a<-a[,-c(1,2)]
  a$pct.used<-paste0(a$pct.used, "%")
  names(a)<-c("Region", "Category", "Total Species", "Removed Species", "Used Species", "Percent Used")

library(magrittr)
library(flextable)
a %>% 
  tibble::rownames_to_column() %>% 
  flextable() %>%
  set_header_labels(rowname = "") %>% 
  # add_header_row(values = c("", "Group 1", "Group 2"), 
  #                colwidths = c(1, 2, 2)) %>% 
  theme_zebra() %>% autofit()
}


keydatatable<-function(Date0, yr, maxyr, folderpattern, dir.output){
  outputrun<-list.files(path = dir.output, pattern = as.character(Date0), full.names = TRUE)
  a<-list.files(path = (list.files(path = paste0(outputrun, "/analyses/"), full.names = TRUE, pattern = paste0(yr, "To", maxyr, "_", folderpattern))), 
                     pattern = "outputtables", full.names = TRUE, ignore.case = TRUE)
  b<-a[(grepl(pattern =paste0(yr, "To"), x = a))]
  b<-list.files(path = b, pattern = "_US_", full.names = TRUE)
  b<-b[grep(pattern = "_Review", x = b)]
  
  # b<-load(paste0(a, "/AllFigures.rdata"))
  a<-read.csv(file = b)
  rownames(a)<-a$X
  a$X<-NULL

  a<-a[,(grepl(pattern = "PI",x = names(a)) | 
          grepl(pattern = "Q[0-9]+_",x = names(a)) | 
          grepl(pattern = "Q_Total",x = names(a)) | 
          grepl(pattern = "QI",x = names(a)))]
  
  aa<-cbind.data.frame(data.frame(a[,grepl(pattern = "Total", x = names(a))]), 
                      data.frame(a[,!(grepl(pattern = "Total", x = names(a)))]))
  names(aa)<-c(names(a)[grepl(pattern = "Total", x = names(a))], 
              names(a)[!(grepl(pattern = "Total", x = names(a)))])
  a<-aa
  groups<-unlist(lapply(strsplit(split = "_", x = names(a)), `[[`, 2))
  names(a)<-gsub(pattern = "[0-9]+", replacement = "", x = names(a))
  names(a)<-gsub(pattern = "_[a-zA-Z]+", replacement = "", x = names(a))

  a[,(names(a) == "Q")]<-a[,(names(a) == "Q")]/1e6
  
  if (sum(names(a) == "PI")>0) {
  for (i in 1:length(which(names(a) == "PI"))){
    a[,which(names(a) == "PI")[i]]<-a[,which(names(a) == "PI")[i]]/a[1,which(names(a) == "PI")[i]]
  }
  }
    for (i in 1:length(which(names(a) == "QI"))){
    a[,which(names(a) == "QI")[i]]<-a[,which(names(a) == "QI")[i]]/a[1,which(names(a) == "QI")[i]]
  }
  
  g<-t(data.frame(table(groups)))
  g<-g[,match(table = g[1,], x = unique(groups))]

library(magrittr)
library(flextable)
a %>% 
  tibble::rownames_to_column() %>% 
  flextable() %>%
  set_header_labels(rowname = "") %>% 
  add_header_row(values = c("", g[1,]),
                 colwidths = c(1, as.numeric(g[2,]))) %>%
   theme_box() %>% autofit()
}

fold<-list.files(path = list.files(path = list.files(paste0(dir.out, "/analyses/"), 
                                                     pattern = folderpattern, 
                                                     full.names = TRUE), 
                                   pattern = "outputtables", 
                                   full.names = TRUE)[3], 
                 full.names = FALSE)[1]

#Find base yr
fold0<-strsplit(x = fold, split = "_")
a<-unique(paste(lapply(fold0, `[[`, 3)))
baseyr<-(gsub(pattern = "byr", replacement = "", x = a))

#Method
fold<-list.files(paste0(dir.out, "/analyses/"), pattern = folderpattern, full.names = FALSE)

fold0<-strsplit(x = fold, split = "_")
a<-unique(paste(lapply(fold0, `[[`, 3)))



if (a == "P") {
  plotpartnames <- c("Q-Category", "QE-Category", "QI-Line", "PI-Line")
  # plotyaxis<-c("Q ")
  method0<-"Price Method"
} else if (a == "Q") {
  plotpartnames <- c("Q-Category", "QI-Line", "QE-Category", "VE-Line")
  method0<-"Quantity Method"
}

```

```{r}
yr<-1950
```

# National `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_US_", 
            folderpattern, plotpartnames, plot, plotyaxis)
```

# Species Percents `r yr`-`r maxyr` (`r method0`)

```{r}
speciestable(Date0, yr, maxyr, folderpattern, dir.output)
```


```{r}
yr<-1997
```

# National `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_US_", 
            folderpattern, plotpartnames, plotyaxis)
```

# Species Percents `r yr`-`r maxyr` (`r method0`)

```{r}
speciestable(Date0, yr, maxyr, folderpattern, dir.output)
```

```{r}
yr<-2007
```

# National `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_US_", 
            folderpattern, plotpartnames, plotyaxis)
```

# Species Percents `r yr`-`r maxyr` (`r method0`)

```{r}
speciestable(Date0, yr, maxyr, folderpattern, dir.output)
```


# Data `r yr`-`r maxyr` (`r method0`)

>Price Index (2007 = 1)

>Implicit Quantity (in 2007 $Million)

```{r}
keydatatable(Date0, yr, maxyr, folderpattern, dir.output)
```

# North Pacific `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_NP_", 
            folderpattern, plotpartnames, plotyaxis)
```

# Pacific `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_Pac_", 
            folderpattern, plotpartnames, plotyaxis)
```

# Western Pacific `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_WP_", 
            folderpattern, plotpartnames, plotyaxis)
```

# New England `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_NE_", 
            folderpattern, plotpartnames, plotyaxis)
```

# Mid-Atlantic `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_MA_", 
            folderpattern, plotpartnames, plotyaxis)
```

# Northeast `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_NorE_", 
            folderpattern, plotpartnames, plotyaxis)
```

# South Atlantic `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_SA_", 
            folderpattern, plotpartnames, plotyaxis)
```

# Gulf of Mexico `r yr`-`r maxyr` (`r method0`)

```{r}
plotkeyfig(yr, 
            place = "_GOM_", 
            folderpattern, plotpartnames, plotyaxis)
```

