---
title: "Measuring Output for U.S. Commercial Fisheries — From Theory to Practice"
author: 'Emily Markowitz^1^ (Emily.Markowitz@noaa.gov) Sun Ling Wang^2^ (Sun-Ling.Wang@noaa.gov) \n\n ^1^Contractor, ECS Federal in support of NOAA Fisheries Office of Science and Technology Economics & Social Analysis Division \n\n ^2^On detail with the NOAA Fisheries Office of Science and Technology Economics & Social Analysis Division \n\n >*The views expressed are those of the author and should not be attributed to the NOAA, ECS or ERS'
date: "`r Sys.Date()`"
output: 
  powerpoint_presentation:
    reference_doc: NOAAFisheriesPowerPointTemplate.pptx
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
#   dev = "svg",
  fig.width = 12,
  fig.height = 7
  # fig.retina = 3
  )

print4plots<-function(plotlist, datadl, title00, legends = c(T,T,T,T), titles = c(F,F,F,F)){

  
  b1<-plotlist[1][[1]]
  if(legends[1] %in% F) {
    b1<-b1 + theme(legend.position = "none")
  }
  if(legends[1] %in% F) {
    b1<-b1 + ggtitle("")
  }
  
  
  b2<-plotlist[2][[1]]
  if(legends[2] %in% F) {
    b2<-b2 + theme(legend.position = "none")
  }
  if(legends[2] %in% F) {
    b2<-b2 + ggtitle("")
  }
  
  b3<-plotlist[3][[1]]
  if(legends[3] %in% F) {
    b3<-b3 + theme(legend.position = "none")
  }
  if(legends[3] %in% F) {
    b3<-b3 + ggtitle("")
  }
  
  b4<-plotlist[4][[1]]
  if(legends[4] %in% F) {
    b4<-b4 + theme(legend.position = "none")
  }
  if(legends[4] %in% F) {
    b4<-b4 + ggtitle("")
  }
  
  b<-plotlist
  layout <- (b1 + b2) / (b3 + b4)
  
  title0<-strsplit(split = "_", x = names(b)[1])[[1]][-c(1,2)]
  title0<-title0[-length(title0)]
  title0<-gsub(pattern = "byr", replacement = "base yr = ", x = title0)
  title0<-paste(title0, collapse = " ")
  title0<-gsub(pattern = " P ", replacement = " Price Method ", x = title0)
  title0<-gsub(pattern = " Q ", replacement = " Quantity Method ", x = title0)
  
  layout +
    plot_annotation(
    title = title00, 
    subtitle = title0,
    caption = paste0("Data downloaded from FOSS ", datadl),
    theme = theme(plot.title = element_text(size = 20, hjust = 0.5, face = "bold"))
    )
}

plotnlines<-function(dat, title00, place){
  
  xnames<-as.numeric(paste0(dat$Year))
  xnames[!(xnames %in% seq(from = min((as.numeric(xnames))),
                           to = max(as.numeric(xnames)),
                           by = 10))]<-""
  
  dat$val<-as.numeric(as.character(dat$val))
  dat$val[(is.infinite(dat$val))]<-NA
  divideby<-paste0("(", strsplit(x = xunits(mean(dat$val, na.rm = T)), split = " ")[[1]][2], "s)")
  if (divideby %in% "(trillions)") {
    divideby0<-1e12
  } else if (divideby %in% "(billions)") {
    divideby0<-1e9
  } else if (divideby %in% "(millions)") {
    divideby0<-1e6
  } else if (divideby %in% "(thousands)") {
    divideby0<-1e3
  } else if (divideby %in% "(NAs)") {
    divideby0<-1
    divideby<-""
  }
  
  dat$val<-dat$val/divideby0
  # ynames<-as.numeric(paste0(val))
  
  g<-ggplot(data = dat, aes(x = factor(Year), y = val, color = cat)) +
    geom_line(aes(group = cat)) +
    geom_point() +
    theme(
      # legend.position = c(0.9, 0.2), 
      panel.grid.major.y = element_line( color=NOAALightBlue, size = .1 ),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      axis.line = element_line( color=NOAALightBlue, size = .1 ),
      axis.ticks = element_blank(), # remove ticks
      panel.background = element_blank()
    )  + 
    ylab(paste0(gsub(pattern = "_", replacement = "", 
                    x = strsplit(x = title00, split = "-")[[1]][1]), 
               " ", divideby)) +
    xlab("Year") +
    scale_x_discrete(labels= xnames) +
    # scale_y_discrete(labels= ynames) +
    guides(fill=FALSE) + 
    ggtitle(paste0(place))
  
  return(g)
}

xunits<-function(temp00, combine=T) {
  
  temp00<-sum(as.numeric(temp00))
  sigfig<-format(temp00, digits = 3, scientific = TRUE)
  sigfig0<-as.numeric(substr(x = sigfig, start = (nchar(sigfig)-1), stop = nchar(sigfig)))
  
  if (sigfig0<=5) {
    # if (sigfig0<4) {
    unit<-""
    x<-format(x = temp00, big.mark = ",", digits = 0, scientific = F)
    # } else if (sigfig0>=4 & sigfig0<6) {
    #   unit<-" thousand"
    # x<-round(temp00/1e3, digits = 1)
    # } else if (sigfig0==5) {
    #   unit<-" thousand"
    #   x<-round(temp00/1e3, digits = 0)
  } else if (sigfig0>=6 & sigfig0<9) {
    unit<-" million"
    x<-round(temp00/1e6, digits = 1)
  } else if (sigfig0>=9 & sigfig0<12) {
    unit<-" billion"
    x<-round(temp00/1e9, digits = 1)
  } else if (sigfig0>=12) {
    unit<-" trillion"
    x<-round(temp00/1e12, digits = 1)
  }
  
  out<-ifelse(combine==T, paste0(x, unit), list(x, unit))
  
  return(out)
}

plotcrossanalysis<-function(dat0, place, datadl){
  
  #Q
  dat<-dat0[,c(1, grep(pattern = "Q ", x = names(dat0)), 
               which(names(dat0) %in% "QE"))]
  
  temp0<-gather(dat, cat, val, 
                names(dat)[2]:names(dat)[length(names(dat))], 
                factor_key = T)  
  
  Q<-plotnlines(dat = temp0, title00 = "Q", place = place)
  
  
  # #QE
  # dat<-dat0[,c(1, grep(pattern = "QE", x = names(dat0)))]
  # 
  # temp0<-gather(dat, cat, val, 
  #               names(dat)[2]:names(dat)[length(names(dat))], 
  #               factor_key = T)  
  # 
  # QE<-plotnlines(dat = temp0, title00 = "QE", place = place)
  
  
  #QI
  dat<-dat0[,c(1, grep(pattern = "QI ", x = names(dat0)), 
               grep(pattern = "QEI", x = names(dat0)))]
  
  temp0<-gather(dat, cat, val, 
                names(dat)[2]:names(dat)[length(names(dat))], 
                factor_key = T)  
  
  QI<-plotnlines(dat = temp0, title00 = "QI", place = place)
  
  
  #PI
  dat<-dat0[,c(1, grep(pattern = "PI ", x = names(dat0)))]
  
  temp0<-gather(dat, cat, val, 
                names(dat)[2]:names(dat)[length(names(dat))], 
                factor_key = T)  
  
  PI<-plotnlines(dat = temp0, title00 = "PI", place = place)
  
  #blank
  blank<-ggplot(dat = data.frame(x=1,y=1), aes(x, y)) + 
      theme(panel.background = element_blank(), 
            axis.title = element_blank(), 
            axis.text = element_blank(), 
            axis.ticks = element_blank()) + 
      ggtitle("")
  
  plotlist<-list("Q" = Q, 
                 "QI" = QI, 
                 "blank" = blank, 
                 # "QE" = QE, 
                 "PI" = PI)
  
  print4plots(plotlist = plotlist, datadl, title00 = place)
  
}

counter<-1
```


# `r reg.order[counter]` `r gsub(pattern = "To", replace = "-", yr)`

```{r}
place<-reg.order[counter]

if (place %in% "Pacific") {
  temp000<-strsplit(x = names(summarydata), split = " ")
  temp000<-unlist(lapply(temp000, `[[`, 1))
  temp000<-strsplit(x = temp000, split = "_")
  temp000<-unlist(lapply(temp000, `[[`, 1))

  
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    temp000 %in% place][[1]]  
} else {
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    grepl(pattern = place, x = names(summarydata))][[1]]
}
plotcrossanalysis(dat0, place, datadl)
counter<-counter+1
```

# `r reg.order[counter]` `r gsub(pattern = "To", replace = "-", yr)`

```{r}
place<-reg.order[counter]

if (place %in% "Pacific") {
  temp000<-strsplit(x = names(summarydata), split = " ")
  temp000<-unlist(lapply(temp000, `[[`, 1))
  temp000<-strsplit(x = temp000, split = "_")
  temp000<-unlist(lapply(temp000, `[[`, 1))

  
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    temp000 %in% place][[1]]  
} else {
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    grepl(pattern = place, x = names(summarydata))][[1]]
}
plotcrossanalysis(dat0, place, datadl)
counter<-counter+1
```


# `r reg.order[counter]` `r gsub(pattern = "To", replace = "-", yr)`

```{r}
place<-reg.order[counter]

if (place %in% "Pacific") {
  temp000<-strsplit(x = names(summarydata), split = " ")
  temp000<-unlist(lapply(temp000, `[[`, 1))
  temp000<-strsplit(x = temp000, split = "_")
  temp000<-unlist(lapply(temp000, `[[`, 1))

  
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    temp000 %in% place][[1]]  
} else {
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    grepl(pattern = place, x = names(summarydata))][[1]]
}
plotcrossanalysis(dat0, place, datadl)
counter<-counter+1
```


# `r reg.order[counter]` `r gsub(pattern = "To", replace = "-", yr)`

```{r}
place<-reg.order[counter]

if (place %in% "Pacific") {
  temp000<-strsplit(x = names(summarydata), split = " ")
  temp000<-unlist(lapply(temp000, `[[`, 1))
  temp000<-strsplit(x = temp000, split = "_")
  temp000<-unlist(lapply(temp000, `[[`, 1))

  
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    temp000 %in% place][[1]]  
} else {
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    grepl(pattern = place, x = names(summarydata))][[1]]
}
plotcrossanalysis(dat0, place, datadl)
counter<-counter+1
```


# `r reg.order[counter]` `r gsub(pattern = "To", replace = "-", yr)`

```{r}
place<-reg.order[counter]

if (place %in% "Pacific") {
  temp000<-strsplit(x = names(summarydata), split = " ")
  temp000<-unlist(lapply(temp000, `[[`, 1))
  temp000<-strsplit(x = temp000, split = "_")
  temp000<-unlist(lapply(temp000, `[[`, 1))

  
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    temp000 %in% place][[1]]  
} else {
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    grepl(pattern = place, x = names(summarydata))][[1]]
}
plotcrossanalysis(dat0, place, datadl)
counter<-counter+1
```


# `r reg.order[counter]` `r gsub(pattern = "To", replace = "-", yr)`

```{r}
place<-reg.order[counter]

if (place %in% "Pacific") {
  temp000<-strsplit(x = names(summarydata), split = " ")
  temp000<-unlist(lapply(temp000, `[[`, 1))
  temp000<-strsplit(x = temp000, split = "_")
  temp000<-unlist(lapply(temp000, `[[`, 1))

  
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    temp000 %in% place][[1]]  
} else {
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    grepl(pattern = place, x = names(summarydata))][[1]]
}
plotcrossanalysis(dat0, place, datadl)
counter<-counter+1
```


# `r reg.order[counter]` `r gsub(pattern = "To", replace = "-", yr)`

```{r}
place<-reg.order[counter]

if (place %in% "Pacific") {
  temp000<-strsplit(x = names(summarydata), split = " ")
  temp000<-unlist(lapply(temp000, `[[`, 1))
  temp000<-strsplit(x = temp000, split = "_")
  temp000<-unlist(lapply(temp000, `[[`, 1))

  
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    temp000 %in% place][[1]]  
} else {
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    grepl(pattern = place, x = names(summarydata))][[1]]
}
plotcrossanalysis(dat0, place, datadl)
counter<-counter+1
```



# `r reg.order[counter]` `r gsub(pattern = "To", replace = "-", yr)`

```{r}
place<-reg.order[counter]

if (place %in% "Pacific") {
  temp000<-strsplit(x = names(summarydata), split = " ")
  temp000<-unlist(lapply(temp000, `[[`, 1))
  temp000<-strsplit(x = temp000, split = "_")
  temp000<-unlist(lapply(temp000, `[[`, 1))

  
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    temp000 %in% place][[1]]  
} else {
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    grepl(pattern = place, x = names(summarydata))][[1]]
}
plotcrossanalysis(dat0, place, datadl)
counter<-counter+1
```


# `r reg.order[counter]` `r gsub(pattern = "To", replace = "-", yr)`

```{r}
place<-reg.order[counter]

if (place %in% "Pacific") {
  temp000<-strsplit(x = names(summarydata), split = " ")
  temp000<-unlist(lapply(temp000, `[[`, 1))
  temp000<-strsplit(x = temp000, split = "_")
  temp000<-unlist(lapply(temp000, `[[`, 1))

  
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    temp000 %in% place][[1]]  
} else {
dat0<-summarydata[grepl(pattern = yr, x = names(summarydata)) &
                    grepl(pattern = place, x = names(summarydata))][[1]]
}
plotcrossanalysis(dat0, place, datadl)
counter<-counter+1
```

